Unsupervised embedding of trajectories captures the latent structure of mobility

### 2020-10-19 paper/current/main.tex
author contribution statement update

%
% Author Contributions
% 
\subsection*{Author Contributions}
Dakota Murray and Jisung Yoon were involved in all stages of data handling, analysis, and writing.
Sadamori Kojaku contributed to the development of the mathematical framework used in this paper.
Rodrigo Costas provided access to and knowledge of the dataset of scientific mobility.
Woo-Sung Jung, Staša Milojević, and Yong-Yeol Ahn provided guidance, mentorship, and conceptualization.
All authors contributed to the preparation of this manuscript.

>>>>

%
% Author Contributions
% 
\subsection*{Author Contributions}
All authors contributed extensively to the work presented in this paper. D. M. and J.Y. were involved in all stages of conceptualization, analysis, and writing, S.K. developed the theoretical framework, R.C. assembled input data, and W.J., S.M., and Y.A. contributed to conceptualization. 
All authors discussed the results and commented on the manuscript at all stages.
